Quantifying the Relationship Between Genetic Diversity and Population Size Suggests Natural Selection Cannot Explain Lewontin's Paradox

### 2021-08-09 manuscript/elife/elife-manuscript.tex
updated ms

Finally, an important caveat is the increase in rate towards the tips could be
caused by measurement noise, or possibly that uncertainty or bias in the
divergence time estimates deep in the tree. Inspecting the lineage pairs that
lead to this increase in rate towards the tips indicates these represent
plausible rate shifts, e.g.  between cosmopolitan and endemic sister species
like \emph{Drosophila simulans} and \emph{Drosophila sechellia}; however,
ruling out measurement noise entirely as an explanation would involve
considering the uncertainty of diversity and population size estimates.

@@

I quantify the effect of linked selection on diversity as the ratio of observed
diversity ($\pi$) to the estimated diversity in the absence of linked selection
($\pi_0$), $R = \nicefrac{\pi}{\pi_0}$. Here, $\pi_0$ would reflect only
demographic history and non-heritable variation in reproductive success. There
are two difficulties in evaluating whether linked selection could resolve
Lewontin's Paradox. The first difficulty is that $\pi_0$ is unobserved.
Previous work has estimated $\pi_0$ using methods that exploit the spatial
heterogeneity in recombination and functional density across the genome to fit
linked selection models that incorporate both hitchhiking and background
selection \citep{Elyashiv2016-vt,Corbett-Detig2015-gt}. The second
difficulty is understanding how $R$ varies across taxa, since we lack
estimates of critical model parameters for most species. Still, I can address a
key question: if diversity levels were determined by census sizes ($\pi_0 =
4N_c \mu$), are the combined effects of background selection and recurrent
hitchhiking sufficient to reduce diversity to observed levels? Furthermore,
does the relationship between census size and predicted diversity under linked
selection across species, $\pi_{BGS+HH} = R \pi_0$, match the observed
relationship in \FIG{pi-Nc}?

Since we lack estimates of key linked selection parameters across species, I
parameterize the hitchhiking and BGS models using estimates from
\emph{Drosophila melanogaster}, a species known to be strongly affected by
linked selection \citep{Sella2009-nx}. Under a generalized model of
hitchhiking and background selection \citep{Elyashiv2016-vt,Coop2012-cd}
and assuming $N_e = N_c$, expected diversity is

\begin{align} 
  \pi_\text{BGS+HH} \approx \frac{\theta}{\nicefrac{1}{B(U, L)} + 2N_c S(\gamma, L, J)} 
  \label{eqn:div} 
\end{align}
%
where $\theta = 4N_c\mu$, $B(U,L)$ is the effect of background selection, and
$S(\gamma, L, J)$ is the rate of coalescence caused by sweeps (c.f.
\cite{Elyashiv2016-vt}, equation 1, \cite{Coop2012-cd} equation 20). Under
background selection models with recombination, the reduction is $B(U,L) =
\exp(\nicefrac{-U}{L})$ where $U$ is the per diploid genome per generation
deleterious mutation rate, and $L$ is the recombination map length
\citep{Hudson1994-oh,Hudson1995-xc,Nordborg1996-nq}. This BGS model is
similar to models of effective population size under polygenic fitness
variation, and can account for other modes of linked selection
(\cite{Robertson1961-ho,Santiago1995-hx,Santiago1998-bs}, see Appendix 
\ref{app:bgs}, \nameref{app:bgs}). The coalescent rate due to sweeps is $S(\gamma, L, J) =
\nicefrac{\gamma}{L} J$, where $\gamma$ is the number of adaptive substitutions
per generation, and $J$ is the probability a lineage is trapped by sweeps as
they occur across the genome (c.f. $J_{2,2}$ in equation 15 of
\cite{Coop2012-cd}).

Parameterizing the model this way, I then set the key parameters that determine
the impact of recurrent hitchhiking and background selection ($\gamma$, $J$,
and $U$) to high values estimated from \emph{Drosophila melanogaster} by
\cite{Elyashiv2016-vt}. My estimate of the adaptive substitutions per
generation ($\gamma_\text{Dmel}$) based Elyashiv et al. implies a rate of
sweeps per basepair of $\nu_\text{BP,Dmel} \approx 2.34 \times 10^{-11}$, which
is close to other estimates from \emph{D.  melanogaster} (see
\FIGSUPP[linksel]{linked-sel-params}A). The rate of deleterious mutations per
diploid genome, per generation is parameterized using the estimate from
Elyashiv et al., $U_\text{Dmel} = 1.6$, which is a bit greater than previous
estimates based on Bateman-Mukai approaches
\citep{Mukai1985-bc,Mukai1988-vs,Charlesworth1987-ab}. Finally, the probability
that a lineage is trapped in a sweep, $J_\text{Dmel}$, is calculated from the
estimated genome-wide average coalescent rate due to sweeps from Elyashiv et
al. (see \FIGSUPP[linksel]{linked-sel-params}B and Methods:
\nameref{sec:methods-reduction} for more details on parameter estimates).
Using these \emph{Drosophila} parameters, I then explore how the predicted
range of diversity levels under background selection and recurrent hitchhiking
varies across species with recombination map length ($L$) and census population
size ($N_c$).

@@

  \figsupp{The observed $\pi$--$N_c$ relationship (points) across species
    compared to the predicted diversity (ribbons) under different modes of
    linked selection and parameters, for a range of mutation rates $\mu =$
    $10^{-8}--10^{-9}$. In both subplots, the gray ribbon is the expected
    diversity if $N_e = N_c$. In (A), the predicted impact on diversity for
    four modes of linked selection are depicted: background selection (purple)
    and hitchhiking (yellow) individually under the parameters in the
    \FIG{linksel}B, and strong background selection (red) where
    $U_\text{strongBGS} = 10 U_\text{Dmel} \approx 16$, and strong recurrent
    hitchhiking, where $\gamma_\text{strongHH} = 10 \gamma_\text{Dmel} \approx
    0.23$. (B) The combined strong background selection and strong hitchhiking
    (orange) compared to the original predicted diversity as in \FIG{linksel}B
(blue).}{\includegraphics[width=\textwidth]{figure_3_alt.pdf}}\label{figsupp:linked-sel-alt}

@@

\figsupp{Comparison of the \emph{Drosophila} sweep parameters used in this study with parameters from other studies.
     (A) The estimate of the number of sweeps per basepair, per genome
      ($\nu_\text{BP}$) from Table 2 of \cite{Elyashiv2016-vt} (the studies
      included are \cite{Li2006-xa,Andolfatto2007-uy,Macpherson2007-qt} and
      \cite{Jensen2008-vz}); the red point is my estimate used in
      this paper. (B) Points are the data from \cite{Shapiro2007-gp}.  The
      blue line is the non-linear least squares fit to the data, and the green
      dashed line is the sweep model parameterized by the genome-wide average
      sweep coalescent rate $2NS \approx 0.92$ from the classic sweep and
      background selection model of \cite{Elyashiv2016-vt} ($r_s$ in
    Supplementary Table S6).}{\includegraphics[width=\textwidth]{linked_sel_params.pdf}}\label{figsupp:linked-sel-params}

@@

Previous work has found that the impact of linked selection increases with
$N_c$ (\cite{Corbett-Detig2015-gt}; see \FIGSUPP[linksel]{reductions}A), and it
is often thought that this is driven by higher rates of adaptive substitutions
in larger populations \citep{Ohta1992-yi}, despite equivocal evidence
\citep{Galtier2016-dq}.  However, there is another mechanism by which species
with larger population sizes might experience a greater impact of linked
selection: recombinational map length, $L$, is known to correlate with body
mass \citep{Burt1987-tq} and thus varies inversely with population size. As
this is a critical parameter that determines the genome-wide impact of both
hitchhiking and background selection, I examine the relationship between
recombination map length ($L$) and census population size ($N_c$) across taxa,
using available estimates of map lengths across species
\citep{Stapley2017-fs,Corbett-Detig2015-gt}. I find a significant non-linear
relationship using phylogenetic mixed-effects models ( \FIG{linksel}A; see
Methods and Materials: \nameref{sec:methods-pcm}).  There is also a correlation
between map length and genome size (\FIGSUPP[linksel]{genome-size-maplen}) and
genome size and population size (\FIGSUPP[linksel]{genome-size-Nc}). These
findings are consistent with both the hypothesis that non-adaptive processes
increase genome size in small-$N_e$ species \citep{Lynch2003-bn} which in turn
could increase map lengths, as well as the hypothesis that map lengths are
adaptively longer to more efficiently select against deleterious alleles
\citep{Roze2021-ya}.  Overall, the negative relationship between map length and
census size indicates linked selection is expected to be stronger in short map
length, high-$N_c$ species.

Then, I predict the expected diversity ($\pi_{BGS+HH}$) under background
selection and hitchhiking, were $N_e= N_c$, and assuming all species had the
rate of sweeps and strength of BGS as \emph{D. melanogaster}. Since neutral
mutation rates $\mu$ are unknown and vary across species, I calculate the range
of predicted $\pi_{BGS+HH}$ estimates for $\mu = 10^{-8}$--$10^{-9}$ (using the
four-alleles model, \cite{Tajima1996-rb}), and compare this to the observed
relationship between $\pi$ and $N_c$ in \FIG{linksel}B.  Under these
parameters, linked selection begins to appreciably depress diversity around
$N_c \approx 10^9$, since $S \approx 10^{-8}$--$10^{-9}$ and linked selection
dominates drift when $S > \nicefrac{1}{2N}$.  Overall, this reveals two
problems for the hypothesis that linked selection could solve Lewontin's
Paradox. First, low to mid-$N_c$ species (census sizes between
$10^{4}$--$10^{10}$) have sufficiently long map lengths that their diversity
levels are only moderately reduced by linked selection, leading to a wide gap
between predicted and observed diversity levels. For this not to be the case,
the parameters that determine the strength of background selection and
recurrent hitchhiking would need to be \emph{higher} among these species than
in \emph{Drosophila melanogaster}. This would require that the rate of adaptive
mutations or the deleterious mutation rate be orders of magnitude higher for
species within this range than in \emph{Drosophila}, which is incompatible with
the rate of adaptive substitutions across species \citep{Galtier2016-dq} and
mutation rates \citep{Lynch2010-ki}. Furthermore, linked selection has been
quantified in humans, which fall in this census size range, and has been found
to be relatively weak
\citep{McVicker2009-ax,Hernandez2011-gs,Hellmann2008-ic,Cai2009-by,Boyko2008-tj}.
Second, while hitchhiking and BGS can reduce predicted diversity levels for
high-$N_c$ species ($N_c > 10^{10}$) to observed levels, this would imply
available estimates of $\pi_0$ are underestimated by several orders of
magnitude in \emph{Drosophila} (\FIGSUPP[linksel]{reductions}B). The high
reductions in $\pi$ predicted here (compared to those of
\cite{Elyashiv2016-vt}) are a result of using $N_c$, rather than $N_e =
\nicefrac{\pi_0}{4 \mu}$ in the denominator of Equation \eqref{eqn:div}, which
leads to a very high rate of sweeps in the population.  I do not consider
selective interference, though the saturation of adaptive substitutions per
Morgan would only act to limit the reduction in diversity
\citep{Weissman2012-aa}, and thus these results are conservative.  Overall,
while linked selection could decouple diversity from census size for high-$N_c$
species, recurrent hitchhiking and background selection seem unlikely to
explain the observed patterns of diversity across species under our
understanding of the range of parameter estimates.

@@

Nearly fifty years after Lewontin's description of the Paradox of Variation,
how evolutionary, life history, and ecological processes interact to constrain
diversity across taxa to a narrow range remains a mystery. I revisit Lewontin's
Paradox by first characterizing the relationship between genomic estimates of
pairwise diversity and approximate census population size across 172 metazoan
species. Previous surveys have used allozyme-based estimates, fewer taxa, or
qualitative measures of population size. My estimates of census population
sizes are quite approximate, since they use body size to predict density. An
improved estimate might consider vagility (as \cite{Soule1976-he} did), though
this is harder to do systematically across many taxa. Future work might also
use other ecological information, such as total biomass, or species
distribution modeling to improve census size estimates
\citep{Bar-On2018-kc,Mora2011-wm}.  Still, it seems more accurate
estimates would be unlikely to change the qualitative findings here, which
resemble those of early surveys \citep{Nei1984-zi,Soule1976-he}.

@@

The predicted reductions in diversity due to linked selection are approximated
using selection and deleterious mutation parameters from \emph{Drosophila
melanogaster}, and the recombination map length estimates from
\cite{Stapley2017-fs} and \cite{Corbett-Detig2015-gt}. The mathematical details
of the simplified sweep model are explained in the Appendix Section
\ref{app:sweep}. I use estimates of the number of substitutions, $m$, in genic
regions between \emph{D.  melanogaster} and \emph{D. simulans} from
\cite{Hu2013-pg}.  Following \cite{Elyashiv2016-vt}, only substitutions in UTRs
and exons are included, since they found no evidence of sweeps in introns.
Then, I average over annotation classes to estimate the mean proportion of
substitutions that are beneficial, $\alpha_\text{Dmel}=0.42$, which are
consistent with the estimates of Elyashiv et al. and estimates from
MacDonald--Kreitman test approaches (see \cite{Eyre-Walker2006-li}, Table 1).
Then, I use divergence time estimates between \emph{D. melanogaster} and
\emph{D. simulans} of $4.2 \times 10^6$ and estimate of ten generations per
year \citep{Obbard2012-on}, calculating there are $\gamma_\text{Dmel} =
\nicefrac{\alpha m}{2T} = 2.26 \times 10^{-3}$ substitutions per generation.
Given the length of the \emph{Drosophila} autosomes, $G$, this implies that the
rate of beneficial substitutions per basepair, per generation is $\nu_{BP,Dmel}
= \nicefrac{\gamma_\text{Dmel}}{G} = 2.34 \times 10^{-11}$. Finally, I estimate
$J_\text{Dmel}$ from the estimate of genome-wide average rate of sweeps from
Elyashiv et al. (Supplementary Table S6) and assuming \emph{Drosophila} $N_e =
10^6$. These \emph{Drosophila melanogaster} hitchhiking parameter estimates are
close to other previously-published estimates
(\FIGSUPP[linksel]{linked-sel-params}). Finally, I use $U_\text{Dmel} = 1.6$,
from \cite{Elyashiv2016-vt}. With these parameter estimates from \emph{D.
melanogaster}, the recombination map lengths across species, and Equation
\eqref{eqn:div}, I estimate $\pi_\text{BGS+HH}$ (assuming $N_c=N_c$) across all
species. This leads to a range of predicted diversity ranges across species
corresponding to $\mu=10^{-8}$--$10^{-9}$; to visualize these, I take a convex
hull of all diversity ranges and smooth this with R's \texttt{smooth.spline}
function.

@@

Since I use \emph{Drosophila melanogaster} parameter estimates from
\cite{Elyashiv2016-vt}, I now reconcile their model's $S$ term with the
simple model above. They estimate $S$ in \emph{Drosophila melanogaster} using a
composite likelihood model that considers hitchhiking and background selection
simultaneously, using substitutions and stratifying by annotation.  For a
neutral position at site $x$, the coalescent rate due to sweeps is given by
Elyashiv et al.'s equation 3,

@@

where the integral is equal to $J$ (c.f. $J_{2,2}$ of equation 15 in
\cite{Coop2012-cd}) since a simple model of $q_f(r) = f \exp(- 2r \tau(s, N))$
and if we condition on fixation, $f = 1$. This expression is useful to
generalize across species, since we know $N$ and $L$. Additionally, we have
estimates of $\alpha$ and $\nicefrac{m}{T}$ in \emph{Drosophila} and other
species. In Elyashiv et al, they consider the number of substitutions per
generation in genic regions only; it should be noted that the number of coding
basepairs varies little across species. For convenience, I define $\gamma =
\nicefrac{\alpha m}{T}$ as the number of adaptive substitutions per generation
per entire genome, such that $S(\gamma, L, J) = \nicefrac{\gamma}{L} \; J$ used
in the main text. Using the estimates of $m \approx 4.5 \times 10^{5}$, $\alpha
\approx 0.42$, and $T \approx 8.4 \times 10^{7}$ from the Supplementary
Material of Elyashiv et al., I arrive at $\gamma \approx 0.00226$ adaptive
substitutions per generation, per genome. For a $\approx 100$ megabase genome,
this translates to a $\nu_\text{BP} \approx 2.34 \times 10^{-11}$, which is
close to previous estimates (Supplementary Figure
\ref{figsupp:linked-sel-params}). For $J$, I use an empirical estimate
calculated from the genome-wide average of the rate of coalescent events due to
sweeps, from Supplementary Table S6 of Elyashiv et al. ($r_s = 2NS \approx
0.92$). This implies $J \approx 4.46 \times 10^{-4}$. Alternatively, I have
tried using the estimated distribution of selection coefficients from Elyashiv
et al., but this led to a weaker estimate of $J$, since the adaptive
substitutions considered tend to cluster around genic regions. Note that these
\emph{Drosophila} sweep parameters I have used are close to previous estimates
(Supplementary Figures \ref{figsupp:linked-sel-params} A and B).

>>>>

Finally, an important caveat is the increase in rate towards the tips could be
caused by measurement noise, or possibly uncertainty or bias in the divergence
time estimates deep in the tree. Inspecting the lineage pairs that lead to this
increase in rate towards the tips indicates these represent plausible rate
shifts, e.g.  between cosmopolitan and endemic sister species like
\emph{Drosophila simulans} and \emph{Drosophila sechellia}; however, ruling out
measurement noise entirely as an explanation would involve modeling the
uncertainty of diversity and population size estimates.

@@

I quantify the effect of linked selection on diversity as the ratio of observed
diversity ($\pi$) to the estimated diversity in the absence of linked selection
($\pi_0$), $R = \nicefrac{\pi}{\pi_0}$. Here, $\pi_0$ would reflect only
demographic history and non-heritable variation in reproductive success. There
are two difficulties in evaluating whether linked selection could resolve
Lewontin's Paradox. The first difficulty is that $\pi_0$ is unobserved.
Previous work has estimated $\pi_0$ using methods that exploit the spatial
heterogeneity in recombination and functional density across the genome to fit
linked selection models that incorporate both hitchhiking and background
selection \citep{Elyashiv2016-vt,Corbett-Detig2015-gt}. The second difficulty
is understanding how $R$ varies across taxa, since we lack estimates of
critical model parameters for most species. Still, I can address a key
question: if diversity levels were determined by census sizes ($\pi_0 = 4N_c
\mu$), would the combined effects of background selection and recurrent
hitchhiking sufficient to reduce diversity to observed levels? Furthermore,
does the relationship between census size and predicted diversity under linked
selection across species, $\pi_{BGS+HH} = R \pi_0$, match the observed
relationship in \FIG{pi-Nc}?

Since we lack estimates of selection parameters across species, I parameterize
the hitchhiking and BGS models using estimates from \emph{Drosophila
melanogaster}, a species known to be strongly affected by linked selection
\citep{Sella2009-nx}. Under a generalized model of hitchhiking and background
selection \citep{Elyashiv2016-vt,Coop2012-cd} and assuming $N_e = N_c$,
the expected diversity is

\begin{align} 
  \pi_\text{BGS+HH} \approx \frac{\theta}{\nicefrac{1}{B(U, L)} + 2N_c S(\gamma, J, L)} 
  \label{eqn:div} 
\end{align}
%
where $\theta = 4N_c\mu$, $B(U,L)$ is the effect of background selection, and
$S(\gamma, J, L)$ is the rate of coalescence caused by sweeps (c.f.
\cite{Elyashiv2016-vt}, equation 1, \cite{Coop2012-cd} equation 20). Under
background selection models with recombination, the reduction is $B(U,L) =
\exp(\nicefrac{-U}{L})$ where $U$ is the per diploid genome per generation
deleterious mutation rate, and $L$ is the recombination map length
\citep{Hudson1994-oh,Hudson1995-xc,Nordborg1996-nq}. This BGS model is
similar to models of effective population size under polygenic fitness
variation, and can account for other modes of linked selection
(\cite{Robertson1961-ho,Santiago1995-hx,Santiago1998-bs}, see Appendix 
\ref{app:bgs}, \nameref{app:bgs}). The coalescence rate due to sweeps is $S(\gamma,J,L) =
\nicefrac{\gamma}{L} J$, where $\gamma$ is the number of adaptive substitutions
per generation, and $J$ is the probability a lineage is trapped by sweeps as
they occur across the genome (c.f. $J_{2,2}$ in equation 15 of
\cite{Coop2012-cd}).

Parameterizing the model this way, I then set the key parameters that determine
the impact of recurrent hitchhiking and background selection ($\gamma$, $J$,
and $U$) to strong selection values estimated for \emph{Drosophila
melanogaster} by \cite{Elyashiv2016-vt}. My estimate of the adaptive
substitutions per generation ($\gamma_\text{Dmel} \approx 2.3 \times 10^{-3}$)
based Elyashiv et al.  implies a rate of sweeps per basepair of
$\nu_\text{BP,Dmel} \approx 2.34 \times 10^{-11}$, which is close to other
estimates from \emph{D.  melanogaster} (see
\FIGSUPP[linksel]{linked-sel-params}A). The rate of deleterious mutations per
diploid genome, per generation is parameterized using the estimate from
Elyashiv et al., $U_\text{Dmel} = 1.6$, which is slightly greater than previous
estimates based on Bateman-Mukai approaches
\citep{Mukai1985-bc,Mukai1988-vs,Charlesworth1987-ab}. Finally, the probability
that a lineage is trapped in a sweep, $J_\text{Dmel} \approx 4.5 \times
10^{-4}$, is calculated from the estimated genome-wide average coalescence rate
due to sweeps from Elyashiv et al. (see \FIGSUPP[linksel]{linked-sel-params}B
and Methods: \nameref{sec:methods-reduction} for more details on parameter
estimates).  Using these parameters, I then explore how the predicted range of
diversity levels varies across species with recombination map length ($L$) and
census population size ($N_c$).

@@

  \figsupp{The observed $\pi$--$N_c$ relationship (points) across species
    compared to the predicted diversity (ribbons) under different modes of
    linked selection and parameters, for a range of mutation rates $\mu =$
    $10^{-8}$--$10^{-9}$. In both subplots, the gray ribbon is the expected
    diversity if $N_e = N_c$. In (A), the predicted impact on diversity for
    four modes of linked selection are depicted: background selection (purple)
    and hitchhiking (yellow) individually under the \emph{Drosophila
    melanogaster} parameters as in \FIG{linksel}B, and strong background
    selection (red) where $U_\text{strongBGS} = 10 U_\text{Dmel} \approx 16$,
    and strong recurrent hitchhiking, where $\gamma_\text{strongHH} = 10
    \gamma_\text{Dmel} \approx 0.23$. (B) The predicted diversity under the
    combined effects of strong background selection and strong hitchhiking
    (orange) compared to the original predicted diversity as in \FIG{linksel}B
    (blue). Overall, under strong background selection and hitchhiking
    parameters, predicted diversity would be less than observed for high-$N_c$
    species, indicating the poor fit to observed data is not sensitive to the choice of
  \emph{Drosophila melanogaster} parameters.}{\includegraphics[width=\textwidth]{figure_3_alt.pdf}}\label{figsupp:linked-sel-alt}

@@

\figsupp{Comparison of the \emph{Drosophila} sweep parameters used in this study with parameters from other studies.
     (A) The estimate of the number of sweeps per basepair, per genome
      ($\nu_\text{BP}$) from Table 2 of \cite{Elyashiv2016-vt} (the studies
      included are \cite{Li2006-xa,Andolfatto2007-uy,Macpherson2007-qt} and
      \cite{Jensen2008-vz}); the red point is my estimate used in
      this paper. (B) Points are the data from \cite{Shapiro2007-gp}.  The
      blue line is the non-linear least squares fit to the data, and the green
      dashed line is the sweep model parameterized by the genome-wide average
      sweep coalescence rate $2NS \approx 0.92$ from the classic sweep and
      background selection model of \cite{Elyashiv2016-vt} ($r_s$ in
    Supplementary Table S6).}{\includegraphics[width=\textwidth]{linked_sel_params.pdf}}\label{figsupp:linked-sel-params}

@@

Previous work has found that the impact of linked selection increases with
$N_c$ (\cite{Corbett-Detig2015-gt}; see \FIGSUPP[linksel]{reductions}A), and it
is often thought that this is driven by higher rates of adaptive substitutions
in larger populations \citep{Ohta1992-yi}, despite equivocal evidence
\citep{Galtier2016-dq}.  However, there is another mechanism by which species
with larger population sizes might experience a greater impact of linked
selection: recombination map length, $L$, is known to correlate with body mass
\citep{Burt1987-tq} and thus varies inversely with population size. As this is
a critical parameter that determines the genome-wide impact of both hitchhiking
and background selection, I examine the relationship between recombination map
length ($L$) and census population size ($N_c$) across taxa, using available
estimates of map lengths across species
\citep{Stapley2017-fs,Corbett-Detig2015-gt}. I find a significant non-linear
relationship using phylogenetic mixed-effects models ( \FIG{linksel}A; see
Methods and Materials: \nameref{sec:methods-pcm}).  There is also a correlation
between map length and genome size (\FIGSUPP[linksel]{genome-size-maplen}) and
genome size and population size (\FIGSUPP[linksel]{genome-size-Nc}). These
findings are consistent with the hypothesis that non-adaptive processes
increase genome size in small-$N_e$ species \citep{Lynch2003-bn} which in turn
could increase map lengths, as well as the hypothesis that map lengths are
adaptively longer to more efficiently select against deleterious alleles
\citep{Roze2021-ya}.  Overall, the negative relationship between map length and
census size indicates linked selection is expected to be stronger in species
with short map lengths, which are high-$N_c$ species.

Then, I predict the expected diversity ($\pi_{BGS+HH}$) under background
selection and hitchhiking, assuming $N_e= N_c$ and that all species had the
rate of sweeps and strength of BGS as \emph{D. melanogaster}. Since neutral
mutation rates $\mu$ are unknown and vary across species, I calculate the range
of predicted $\pi_{BGS+HH}$ estimates for $\mu = 10^{-8}$--$10^{-9}$ (using the
four-alleles model, \cite{Tajima1996-rb}), and compare this to the observed
relationship between $\pi$ and $N_c$ in \FIG{linksel}B.  Under these parameters
and assumptions, linked selection begins to appreciably constrain diversity for
$N_c \gtrsim 10^7$, since $S(\gamma_\text{Dmel}, J_\text{Dmel}, L) \approx
10^{-7}$--$10^{-8}$ and linked selection dominates drift when $S(\gamma, J, L)
> \nicefrac{1}{2N}$. Overall, this reveals two problems for the hypothesis that
linked selection could solve Lewontin's Paradox. First, low to mid-$N_c$
species (census sizes between $10^{4}$--$10^{7}$) have sufficiently long map
lengths that their diversity levels are only moderately reduced by linked
selection, leading to a wide gap between predicted and observed diversity
levels. For this not to be the case, the rate of adaptive mutations or the
deleterious mutation rate would need to be orders of magnitude higher for
species within this range than in \emph{Drosophila melanogaster}, which is
incompatible with the rate of adaptive protein substitutions across species
\citep{Galtier2016-dq} and overall mutation rates \citep{Lynch2010-ki}.
Furthermore, linked selection has been quantified in humans, which fall in this
census size range, and has been found to be relatively weak
\citep{McVicker2009-ax,Hernandez2011-gs,Hellmann2008-ic,Cai2009-by,Boyko2008-tj}.
Second, while hitchhiking and BGS can reduce predicted diversity levels for
high-$N_c$ species ($N_c > 10^{12}$) to observed levels, this would imply
available estimates of $\pi_0$ are underestimated by several orders of
magnitude in \emph{Drosophila} (\FIGSUPP[linksel]{reductions}B). The high
reductions in $\pi$ predicted here (compared to those of
\cite{Elyashiv2016-vt}) are a result of using $N_c$, rather than $N_e =
\nicefrac{\pi_0}{4 \mu}$ in the denominator of Equation \eqref{eqn:div}, which
leads to a very high rate of sweeps in the population.  I do not consider
selective interference, though the saturation of adaptive substitutions per
Morgan would only act to limit the reduction in diversity
\citep{Weissman2012-aa}, and thus these results are conservative.  Overall,
while linked selection could decouple diversity from census size for high-$N_c$
species, recurrent hitchhiking and background selection seem unlikely to
explain the observed patterns of diversity across species under our
understanding of the range of parameter estimates.

@@

Nearly fifty years after Lewontin's description of the Paradox of Variation,
how evolutionary, life history, and ecological processes interact to constrain
diversity across taxa to a narrow range remains a mystery. I revisit Lewontin's
Paradox by first characterizing the relationship between genomic estimates of
pairwise diversity and approximate census population size across 172 metazoan
species. Previous surveys have used allozyme-based estimates, fewer taxa, or
proxies of population size. My estimates of census population sizes are rough
approximates, since they use body size to predict density. An improved estimate
might account for vagility (as \cite{Soule1976-he} did), though this is harder
to do systematically across many taxa. Future work might also use other
ecological information, such as total biomass, or species distribution modeling
to improve census size estimates \citep{Bar-On2018-kc,Mora2011-wm}.  Still, it
seems more accurate estimates would be unlikely to change the qualitative
findings here, which resemble those of early surveys
\citep{Nei1984-zi,Soule1976-he}.

@@

The predicted reductions in diversity due to linked selection are approximated
using selection and deleterious mutation parameters from \emph{Drosophila
melanogaster}, and the recombination map length estimates from
\cite{Stapley2017-fs} and \cite{Corbett-Detig2015-gt}. The mathematical details
of the simplified sweep model are explained in the Appendix Section
\ref{app:sweep}. I use estimates of the number of substitutions, $m$, in genic
regions between \emph{D.  melanogaster} and \emph{D. simulans} from
\cite{Hu2013-pg}.  Following \cite{Elyashiv2016-vt}, only substitutions in UTRs
and exons are included, since they found no evidence of sweeps in introns.
Then, I average over annotation classes to estimate the mean proportion of
substitutions that are beneficial, $\alpha_\text{Dmel}=0.42$, which are
consistent with the estimates of Elyashiv et al. and estimates from
MacDonald--Kreitman test approaches (see \cite{Eyre-Walker2006-li}, Table 1).
Then, I use divergence time estimates between \emph{D. melanogaster} and
\emph{D. simulans} of $4.2 \times 10^6$ and estimate of ten generations per
year \citep{Obbard2012-on}, calculating there are $\gamma_\text{Dmel} =
\nicefrac{\alpha m}{2T} = 2.26 \times 10^{-3}$ substitutions per generation.
Given the length of the \emph{Drosophila} autosomes, $G$, this implies that the
rate of beneficial substitutions per basepair, per generation is $\nu_{BP,Dmel}
= \nicefrac{\gamma_\text{Dmel}}{G} = 2.34 \times 10^{-11}$. Finally, I estimate
$J_\text{Dmel} \approx 4.5 \times 10^{-4}$ from the estimate of genome-wide
average rate of sweeps from Elyashiv et al. (Supplementary Table S6) and
assuming \emph{Drosophila} $N_e = 10^6$. These \emph{Drosophila melanogaster}
hitchhiking parameter estimates are close to other previously-published
estimates (\FIGSUPP[linksel]{linked-sel-params}). Finally, I use $U_\text{Dmel}
= 1.6$, from \cite{Elyashiv2016-vt}. With these parameter estimates from
\emph{D.  melanogaster}, the recombination map lengths across species, and
Equation \eqref{eqn:div}, I estimate $\pi_\text{BGS+HH}$ (assuming $N_c=N_c$)
across all species. This leads to a range of predicted diversity ranges across
species corresponding to $\mu=10^{-8}$--$10^{-9}$; to visualize these, I take a
convex hull of all diversity ranges and smooth this with R's
\texttt{smooth.spline} function.

@@

Since I use \emph{Drosophila melanogaster} parameter estimates from
\cite{Elyashiv2016-vt}, I now reconcile their model's $S$ term with the
simple model above. They estimate $S$ in \emph{Drosophila melanogaster} using a
composite likelihood model that considers hitchhiking and background selection
simultaneously, using substitutions and stratifying by annotation.  For a
neutral position at site $x$, the coalescence rate due to sweeps is given by
Elyashiv et al.'s equation 3,

@@

where the integral is equal to $J$ (c.f. $J_{2,2}$ of equation 15 in
\cite{Coop2012-cd}) since a simple model of $q_f(r) = f \exp(- 2r \tau(s, N))$
and if we condition on fixation, $f = 1$. This expression is useful to
generalize across species, since we know $N$ and $L$. Additionally, we have
estimates of $\alpha$ and $\nicefrac{m}{T}$ in \emph{Drosophila} and other
species. In Elyashiv et al, they consider the number of substitutions per
generation in genic regions only; it should be noted that the number of coding
basepairs varies little across species. For convenience, I define $\gamma =
\nicefrac{\alpha m}{T}$ as the number of adaptive substitutions per generation
per entire genome, such that $S(\gamma, J, L) = \nicefrac{\gamma}{L} \; J$ used
in the main text. Using the estimates of $m \approx 4.5 \times 10^{5}$, $\alpha
\approx 0.42$, and $T \approx 8.4 \times 10^{7}$ from the Supplementary
Material of Elyashiv et al., I arrive at $\gamma \approx 0.00226$ adaptive
substitutions per generation, per genome. For a $\approx 100$ megabase genome,
this translates to a $\nu_\text{BP} \approx 2.34 \times 10^{-11}$, which is
close to previous estimates (Supplementary Figure
\ref{figsupp:linked-sel-params}). For $J$, I use an empirical estimate
calculated from the genome-wide average of the rate of coalescent events due to
sweeps, from Supplementary Table S6 of Elyashiv et al. ($r_s = 2NS \approx
0.92$). This implies $J \approx 4.46 \times 10^{-4}$. Alternatively, I have
tried using the estimated distribution of selection coefficients from Elyashiv
et al., but this led to a weaker estimate of $J$, since the adaptive
substitutions considered tend to cluster around genic regions. Note that these
\emph{Drosophila} sweep parameters I have used are close to previous estimates
(Supplementary Figures \ref{figsupp:linked-sel-params} A and B).
